### 2023-09-02 chapters/background.tex
Minor updates

While the papers in this thesis were written to be self-contained, page limits and the need to maintain a specific focus, forced us to limit the scope of technical background each paper provides. In this chapter, we present a more in-depth overview of the technical background relevant to the papers in this thesis. 
We start by introducing the concept of uncertainty, and how it relates to information and probability. We then introduce the task of out-of-distribution detection and a few ways to tackle it.
Then, we present variational autoencoders, and how they can be used to learn representations of speech. Finally, we introduce the concept of self-supervised learning.

>>>>

While the papers in this thesis were written to be self-contained, page limits and the need to maintain a specific focus, forced us to limit the scope of technical background each paper provides. In this chapter, we present a more in-depth overview of the technical background relevant to the papers in this thesis. 
We start by quantifying the concept of uncertainty, and how it relates to information and probability. We then introduce the task of out-of-distribution detection and a few ways to tackle it. 
Then, we present variational autoencoders, and how they can be used to learn representations of speech. Finally, we introduce the concept of self-supervised learning and highlight important differences to variational autoencoders.

### 2023-09-02 chapters/discussion.tex
Update
Write introduction, revise title and some formatting
Write more on the introduction
Minor updates

\section{\cref{chp:paper-hierarchical} revisited: \dots}

\lesstodo[inline]{Discuss sensitivity to ``implicit" prior such as architecture (and probably optimization method and other). Include reference to \cite{huszar_is_2017} discussing the usefulness of using a maximum likelihood objective for representation learning in generative models.}

\section{\cref{chp:paper-review} revisited: \dots}

@@

>>>>

\section{\Cref{chp:paper-hierarchical} revisited: \dots}

\lesstodo[inline]{Discuss sensitivity to ``implicit" prior such as architecture (and probably optimization method and other). Include reference to \cite{huszar_is_2017} discussing the usefulness of using a maximum likelihood objective for representation learning in generative models.}
\lesstodo[inline]{Discuss whether VAEs are even suitable for representation learning due to them minimzing a mutual information term in the ELBO (derive this form).}
\lesstodo[inline]{Discuss some recent work e.g. \cref{morningstar_density_2021}}

\section{\Cref{chp:paper-review} revisited: \dots}

@@

\section{\Cref{chp:paper-retrospective} revisited: \dots}

\lesstodo[inline]{Discuss the calibration of the stroke model and report calibration curve.}
\lesstodo[inline]{Report the results of calibrating the stroke model using e.g. Platt scaling or Isotonic scaling.} % https://scikit-learn.org/stable/modules/calibration.html

### 2023-09-02 chapters/introduction.tex
Minor updates

\subsection{Understanding uncertainty}
% 
% OUTLINE: Introduce aleatoric and epistemic uncertainty. 
% - Discuss the distinction between them and how they relate to the problem of uncertainty estimation in machine learning.
% - 
% 
%
The distinction in uncertainty estimation between known and unknown unknowns is sometimes referred to in terms of \textit{aleatoric uncertainty} and \textit{epistemic uncertainty} \cite{kendall_what_2017}. Both categories of uncertainty are usually used to describe uncertainties in a model's predictions or the model itself including its parameters, but they differ in their sources. 
Aleatoric uncertainty (from latin (aleatorius) 'dice player' or 'gambler') refers to uncertainty in the data itself due to true randomness which is irreducible even with infinite data. 
Epistemic uncertainty (from Greek (epistḗmē) 'knowledge') refers to uncertainty due to things one could in principle know but does not in practice. 
% It could arise because a measurement is not accurate, because the model neglects certain effects, or because particular data have been deliberately hidden. 
Epistemic uncertainty is sometimes referred to as \textit{systematic uncertainty} and aleatoric uncertainty as \textit{stochastic uncertainty} \cite{kendall_what_2017}. 
%, or, \textit{reducible} and \textit{irreducible} uncertainty, respectively. This latter terminology is somewhat misleading since epistemic uncertainty might not be reducible by additional data collection if the model is not sufficiently expressive to represent the data distribution, and aleatoric uncertainty is not necessarily irreducible if we can reduce inherent noise by improving the instruments used to collect the data \cite{kendall_what_2017}. 
Although the distinction between aleatoric and epistemic uncertainty is important, it is not always useful. For instance, a model may be uncertain about a particular prediction due to any of these two kinds of uncertainty. For that reason, the quantity of interest is usually the ``total" uncertainty, often referred to as \textit{predictive uncertainty}, which is simply the combined epistemic and aleatoric uncertainties.

>>>>

\subsection{Understanding uncertainty}
% 
% OUTLINE: Introduce aleatoric and epistemic uncertainty. 
% - Discuss the distinction between them and how they relate to the problem of uncertainty estimation in machine learning.
% - 
% 
%
The distinction in uncertainty estimation between known and unknown unknowns is sometimes referred to in terms of \textit{aleatoric uncertainty} and \textit{epistemic uncertainty} \cite{kendall_what_2017}. Both categories of uncertainty are usually used to describe uncertainties in a model's predictions or the model itself including its parameters, but they differ in their sources. 
Aleatoric uncertainty (from Latin (aleatorius) 'dice player' or 'gambler') refers to uncertainty in the data itself due to true randomness which is irreducible even with infinite data. 
Epistemic uncertainty (from Greek (epistḗmē) 'knowledge') refers to uncertainty due to things one could in principle know but does not in practice. 
% It could arise because a measurement is not accurate, because the model neglects certain effects, or because particular data have been deliberately hidden. 
Epistemic uncertainty is sometimes referred to as \textit{systematic uncertainty} and aleatoric uncertainty as \textit{stochastic uncertainty} \cite{kendall_what_2017}. 
%, or, \textit{reducible} and \textit{irreducible} uncertainty, respectively. This latter terminology is somewhat misleading since epistemic uncertainty might not be reducible by additional data collection if the model is not sufficiently expressive to represent the data distribution, and aleatoric uncertainty is not necessarily irreducible if we can reduce inherent noise by improving the instruments used to collect the data \cite{kendall_what_2017}. 
Although the distinction between aleatoric and epistemic uncertainty is important, it is not always useful. For instance, a model may be uncertain about a particular prediction due to any of these two kinds of uncertainty. For that reason, the quantity of interest is usually the ``total" uncertainty, often referred to as \textit{predictive uncertainty}, which is simply the combined epistemic and aleatoric uncertainties.
